### 2023-02-15 chapter2/chapter2.tex
Updated section formatting in remaining files

\begin{abstract}
\noindent
Abstract text for this chapter
\end{abstract}

\section*{Introduction}
Here's where my chapter on evolutionary analyses will go!

\section*{Results}

\section*{Discussion}

\section*{Materials and methods}

>>>>

\begin{abstract}
\noindent
Here's where my abstract will go!
\end{abstract}

\section{Introduction}
Here's where my introduction will go!

\section{Results}
Here's where my results will go!

\section{Discussion}
Here's where my discussion will go!

\section{Materials and methods}
Here's where my materials and methods will go!

### 2023-02-15 chapter3/chapter3.tex
Updated section formatting in remaining files

\section*{Introduction}
Most code written for data analysis is \textit{ad hoc}, that is, it is intended to accomplish a single task and cannot be used for any other purpose. However, often solving one problem entails solving several other problems along the way, and sometimes those intermediate solutions are general enough to be widely useful. This happened twice over the course of this work, both times involving fitting probabilistic models to data. The first was mixture models, which describe data that contain several subpopulations, each with its own statistical properties, mixed together. For example, in exam scores there are often two clusters: the high-scoring group of students who understood the material and the low-scoring group who did not. The second was hidden Markov models (HMMs), which like mixture models, describe data with several subpopulations. However, in HMMs the data are ordered in a ``time series'' and observations from a given subpopulation tend to occur consecutively. These models are frequently used to analyze systems which toggle between different states over time, for example periods of growth and recession in the economy.

>>>>

\section{Introduction}
Most code written for data analysis is \textit{ad hoc}, that is, it is intended to accomplish a single task and cannot be used for any other purpose. However, often solving one problem entails solving several other problems along the way, and sometimes those intermediate solutions are general enough to be widely useful. This happened twice over the course of this work, both times involving fitting probabilistic models to data. The first was mixture models, which describe data that contain several subpopulations, each with its own statistical properties, mixed together. For example, in exam scores there are often two clusters: the high-scoring group of students who understood the material and the low-scoring group who did not. The second was hidden Markov models (HMMs), which like mixture models, describe data with several subpopulations. However, in HMMs the data are ordered in a ``time series'' and observations from a given subpopulation tend to occur consecutively. These models are frequently used to analyze systems which toggle between different states over time, for example periods of growth and recession in the economy.
